### 2019-06-14 2-Chapters/3-Chapter/chapter3.tex
Added figures of Chapter SMPyBandits

\TODOL{Analyser les expériences les plus récentes et décrire mieux en 3.2, et refaire toutes les courbes pour 3.2 et 3.3}

@@

\begin{figure}[h!]  % [htbp]
	% \centering
	% \includegraphics[width=1.10\linewidth]{16_different_algorithms__lognormregret_vs_arms__56pb__7Ks_T50000.pdf}
	\includegraphics[width=1.10\linewidth]{16_different_algorithms__lognormregret_vs_arms__16pb__T5000.pdf}
	\caption[Regret vs different values of $K$.]{
        Regret vs different values of $K$ ($R_T / \log(T)$),
        for $T=5000$ and for $16$ algorithms.
        The $y$-axis is in log-scale.
        All algorithms appear to have a regret slowly growing with respect to $K$, as predicted by the regret bounds which are linear with respect to the number of arms, as predicted.
        \textsc{Tsallis-Inf} is the only state-of-the-art algorithm which appears to be very inefficient for problems with a small number of arms.
        Both the $\varepsilon$-greedy and Explore-then-Commit algorithms performed poorly, achieving linear regret (not displayed).
	}
	\label{fig:3:16_different_algorithms__lognormregret_vs_arms__16pb__T5000}
\end{figure}

\begin{figure}[h!]  % [htbp]
	% \centering
	% \includegraphics[width=1.10\linewidth]{16_different_algorithms__normregret_vs_horizons__56pb__K32_7Ts.pdf}
	\includegraphics[width=1.10\linewidth]{16_different_algorithms__lognormregret_vs_times__16pb__K8.pdf}
	\caption[Regret vs different values of $T$.]{
        Regret vs different values of $T$ ($R_T / K$),
        for $K=32$ and for $16$ algorithms.
        All efficient algorithms appear to have a logarithmic regret, meaning that their regret bound is indeed logarithmic with respect to the horizon, as predicted.
        The respective ranking of all the algorithms also appears to remain preserved for different values of $T$, which is also backed-up by theoretical results: if two algorithms $\cA$ and $\cA'$ has a regret close to their regret bounds, of the form $R_T \leq \cO(K \log(T))$, and the bound for $\cA$ use a smaller constant than the bound for $\cA'$, $\cA$ should obtain a smaller regret than $\cA'$ no matter the horizon.
        Finally, we also observe once more than both the $\varepsilon$-greedy and Explore-then-Commit algorithms performed poorly, achieving linear regret (not displayed after $T=100000$).
	}
	\label{fig:3:16_different_algorithms__lognormregret_vs_times__16pb__K8}
\end{figure}

\paragraph{Summary of the experiments.}
%
In the two Figures~\ref{fig:3:16_different_algorithms__lognormregret_vs_arms__16pb__T5000} and \ref{fig:3:16_different_algorithms__lognormregret_vs_times__16pb__K8}
included in this section,
we are able to check empirically that the regret of all the efficient algorithm indeed scales as predicted by the theory, that is
linearly in the number of arms, and logarithmically in the horizon, \ie, $R_T = \bigO{K \log T}$.
%
The main take-away message is the following: in all the rest of this thesis, we focus on two algorithms depending if simplicity or efficiency is favored:
\begin{itemize}\tightlist
    \item
    \UCB{} (or Thompson sampling) is used in the more applied Chapter~\ref{chapter:4}, when simplicity is favored,
    \item
    \klUCB{} is used, in the two more theoretical Chapters~\ref{chapter:5} and \ref{chapter:6}, when efficiency is favored, and when we analyze mathematically the performance of an algorithm that is running on top of a classical stationary MAB policy, like our two contributions, \MCTopM{} and \GLR.
\end{itemize}

@@

In Figure~\ref{fig:3:16_different_algorithms__lognormregret_vs_logtime__28pb}, we can see FIXME

@@

In Figure~\ref{fig:3:16_different_algorithms__lognormregret_vs_logmemory__28pb}, we can see FIXME

@@

\begin{figure}[h!]  % [htbp]
	% \centering
	% \includegraphics[width=1.10\linewidth]{16_different_algorithms__normmemory_vs_horizons__56pb__K32_7Ts.pdf}
	\includegraphics[width=1.10\linewidth]{16_different_algorithms__lognormmemory_vs_times__16pb__K8.pdf}
	\caption[Normalized memory cost vs different values of $T$.]{
        Normalized memory cost vs different values of $T$ ($\cM_T / K$),
        for $K=32$ and for $16$ algorithms.
        $y$-axis is in log-scale.
        All algorithms (except BESA) has a very slowly growing normalized memory cost, meaning that for $T$ rounds they use a computation time almost independent of $T$, as predicted: $\cM_T = \bigO{K}$.
        There is a clear separation between three groups.
        First, BESA is very costly in terms of memory, and $\UCB\dagger$ and \textsc{Tsallis-Inf} are also more costly than others, and both experiences a linear growth of their memory cost.
        Then, we see PHE, $\mathrm{Exp}3^{++}$, Bayes-UCB and AdBandits having a small but linear growth of memory cost, and it can be explained for each of them (\eg, for Bayes-UCB, computing the $1-1/t$ quantile at time $t$ becomes more and more costly as $t$ grows, and thus as $T$ grows,  ).
        Finally, the other algorithms (including \UCB, \klUCB{} and Thompson sampling) have a very small footprint and their memory cost do not grow much when $T$ increases.
	}
	\label{fig:3:16_different_algorithms__lognormmemory_vs_times__16pb__K8}
\end{figure}

@@

@@

\newpage  % WARNING
% ----------------------------------------------------------------------------
\section{Conclusion}
\label{sec:3:conclusion}

@@

\textbf{Bash command to run these experiments.}
We give below in Code~\ref{lst:3:BashCodeToLaunchLargeExperiments} a Bash command to run the experiments presented in Sections~\ref{sec:3:reviewSPAlgorithms} and \ref{sub:3:additionalExperiments}.
It uses \texttt{for} loops and environment variables from Bash, and not Python, but we could also have done the same by writing a Python script that calls the \texttt{main.py} script for the different values of $N$, $T$ and $K$.

% https://tex.stackexchange.com/a/12430/
\begin{listing}[h!]
    \begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{bash}
$ for N in 4 100 1000;        do \
    for T in $(seq 5000 5000 50000); do \
      for K in $(seq 2 2 32); do \
        DEBUG=False NOPLOTS=False SAVEALL=True N_JOBS=-1 \
          N=$N BAYES=True  T=$T K=$K \
          python3 main.py configuration.py \
        && cp logs/main_py3_log.txt \
              logs/main_py3_log__N${N}_BAYES_T{T}_K{K}.txt \
  done; done; done
    \end{minted}
    \caption{Bash code to run the large experiments presented in Sections~\ref{sec:3:reviewSPAlgorithms} and \ref{sub:3:additionalExperiments}.}
    % \captionof{listing}{Small snippet of Bash code to run an experiment \label{lst:3:BashCodeToLaunchLargeExperiments}.}
    \label{lst:3:BashCodeToLaunchLargeExperiments}
\end{listing}

>>>>

\TODOL{Si j'ai le temps, je peux améliorer les expériences faites en 3.3 et 3.4. C'est déjà suffisant comme ça, je peux juste faire mieux !}

@@

\begin{figure}[h!]  % [htbp]
	% \centering
	% \includegraphics[width=1.10\linewidth]{16_different_algorithms__lognormregret_vs_arms__56pb__7Ks_T50000.pdf}
	\includegraphics[width=1.10\linewidth]{16_different_algorithms__lognormregret_vs_arms__16pb__T5000.pdf}
	\caption[Regret vs different values of $K$.]{
        Regret vs different values of $K$ ($R_T / \log(T)$),
        for $T=5000$ and for $16$ algorithms.
        The $y$-axis is in log-scale.
        All algorithms appear to have a regret slowly growing with respect to $K$, as predicted by the regret bounds which are linear with respect to the number of arms, as predicted.
        Bayesian algorithms appear to be the most efficient, and \klUCB{} as well as \UCB{} are also shown to be efficient.
        % \textsc{Tsallis-Inf} is the only state-of-the-art algorithm which appears to be very inefficient for problems with a small number of arms.
        Both the $\varepsilon$-greedy and Explore-then-Commit algorithms performed poorly, actually they achieve linear regret.
        % (not displayed).
	}
	\label{fig:3:16_different_algorithms__lognormregret_vs_arms__16pb__T5000}
\end{figure}

\begin{figure}[h!]  % [htbp]
	% \centering
	% \includegraphics[width=1.10\linewidth]{16_different_algorithms__normregret_vs_horizons__56pb__K32_7Ts.pdf}
	\includegraphics[width=1.10\linewidth]{16_different_algorithms__lognormregret_vs_times__16pb__K8.pdf}
	\caption[Regret vs different values of $T$.]{
        Regret vs different values of $T$ ($R_T / K$),
        for $K=32$ and for $16$ algorithms.
        All efficient algorithms appear to have a logarithmic regret with respect to the horizon, as predicted.
        The respective ranking of all the algorithms also appears to remain preserved for different values of $T$, which is also backed-up by theoretical results: if two algorithms $\cA$ and $\cA'$ has a regret close to their regret bounds, of the form $R_T \leq \cO(K \log(T))$, and the bound for $\cA$ use a smaller constant than the bound for $\cA'$, $\cA$ should obtain a smaller regret than $\cA'$ no matter the horizon.
        Bayesian algorithms appear to be the most efficient, and \klUCB{} as well as \UCB{} are also shown to be efficient.
        Finally, we also observe once more than both the $\varepsilon$-greedy and Explore-then-Commit algorithms performed poorly, achieving linear regret.
	}
	\label{fig:3:16_different_algorithms__lognormregret_vs_times__16pb__K8}
\end{figure}

\paragraph{Summary of the experiments.}
%
In the two Figures~\ref{fig:3:16_different_algorithms__lognormregret_vs_arms__16pb__T5000} and \ref{fig:3:16_different_algorithms__lognormregret_vs_times__16pb__K8}
included in this section,
we are able to check empirically that the regret of all the efficient algorithm indeed scales as predicted by the theory, that is
linearly in the number of arms, and logarithmically in the horizon, \ie, $R_T = \bigO{K \log T}$.
%
The main take-away message is the following: in all the rest of this thesis, we focus on two algorithms depending if simplicity or efficiency is favored:
\begin{itemize}\tightlist
    \item
    \UCB{} is used in the more applied Chapter~\ref{chapter:4}, when simplicity is favored,
    \item
    \klUCB{} is used, in the two more theoretical Chapters~\ref{chapter:5} and \ref{chapter:6}, when efficiency is favored, and when we analyze mathematically the performance of an algorithm that is running on top of a classical stationary MAB policy, like our two contributions, \MCTopM{} and \GLR.
\end{itemize}

@@

In Figure~\ref{fig:3:16_different_algorithms__lognormregret_vs_logtime__28pb}, we can see that Bayesian algorithms appear to be the most efficient (\ie, in the bottom left corner), and \klUCB{} is very close to their best empirical performances.
\UCB, algorithms that were proven to perform similarly to \UCB{} (\ie, PHE and RCB), and other index policies inspired by \UCB{} (ApprFHG, $\UCB\dagger$) enjoy very similar performances: a larger regret than Bayesian algorithms and \klUCB, but a shorter running time.
%
This highlights a trade-off between optimality in terms of regret and computational efficiency.

@@

Like for the computational cost discussed above,
in Figure~\ref{fig:3:16_different_algorithms__lognormregret_vs_logmemory__28pb}, we can see that Bayesian algorithms like Thompson sampling again appear to be the most efficient (\ie, in the bottom left corner), and \klUCB{} is close to their best empirical performances.
\UCB{} and other index policies inspired by \UCB{} (ApprFHG, $\UCB\dagger$) enjoy very similar performances: a larger regret than Bayesian algorithms and \klUCB, but a similar memory cost.
%
This time, there is no clear trade-off between optimality in terms of regret and memory cost, and based on simply this Figure~\ref{fig:3:16_different_algorithms__lognormregret_vs_logmemory__28pb}, one could advise to use Thompson sampling rather than \klUCB.

@@

\begin{figure}[h!]  % [htbp]
	% \centering
	% \includegraphics[width=1.10\linewidth]{16_different_algorithms__normmemory_vs_horizons__56pb__K32_7Ts.pdf}
	\includegraphics[width=1.10\linewidth]{16_different_algorithms__lognormmemory_vs_times__16pb__K8.pdf}
	\caption[Normalized memory cost vs different values of $T$.]{
        Normalized memory cost vs different values of $T$ ($\cM_T / K$),
        for $K=32$ and for $16$ algorithms.
        $y$-axis is in log-scale.
        All algorithms have a growing normalized memory cost, meaning that for $T$ rounds they use a computation time almost independent of $T$, as predicted: $\cM_T = \bigO{K}$.
        % All algorithms (except BESA) have a very slowly growing normalized memory cost, meaning that for $T$ rounds they use a computation time almost independent of $T$, as predicted: $\cM_T = \bigO{K}$.
        % There is a clear separation between three groups.
        % First, BESA is very costly in terms of memory, and $\UCB\dagger$ and \textsc{Tsallis-Inf} are also more costly than others, and both experiences a linear growth of their memory cost.
        % Then, we see PHE, $\mathrm{Exp}3^{++}$, Bayes-UCB and AdBandits having a small but linear growth of memory cost, and it can be explained for each of them (\eg, for Bayes-UCB, computing a quantile at time $t$ becomes more and more costly as $t$ grows, and thus as $T$ grows,  ).
        % Finally, the other algorithms (including \UCB, \klUCB{} and Thompson sampling) have a very small footprint and their memory cost do not grow much when $T$ increases.
	}
	\label{fig:3:16_different_algorithms__lognormmemory_vs_times__16pb__K8}
\end{figure}

@@

We also shown a trade-off between optimality in terms of regret, and efficiency in terms of time complexity or memory cost.
Our position regarding this trade-off is motivated by Occam's razor principle.
On the first hand, if the algorithm should be implemented on a cognitive radio device that has limited hardware capacity (for instance),
one can reasonably aim at the simplest yet order-optimal algorithms, and we advise to use \UCB{} and algorithms running on top of this simple index policy, as we do in Chapter~\ref{chapter:4}.
On the other hand, if one is more interested in the mathematical developments and wants to prove the tightest possible regret upper bounds, aiming at more efficient but more complex algorithms is interesting, and we chose the \klUCB{} algorithm in Chapters~\ref{chapter:5} and \ref{chapter:6}.

@@

\newpage  % WARNING
\newpage  % WARNING
% ----------------------------------------------------------------------------
\section{Conclusion}
\label{sec:3:conclusion}

@@

\textbf{Bash command to run these experiments.}
We give below in Code~\ref{lst:3:BashCodeToLaunchLargeExperiments} a Bash command to run the experiments presented in Sections~\ref{sec:3:reviewSPAlgorithms} and \ref{sub:3:additionalExperiments}.
It uses \texttt{for} loops and environment variables from Bash, and not Python, but we could also have done the same by writing a Python script that calls the \texttt{main.py} script for the different values of $T$ and $K$.

% https://tex.stackexchange.com/a/12430/
\begin{listing}[h!]
    \begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{bash}
$ for T in $(seq 5000 5000 50000); do \
      for K in $(seq 2 2 32); do \
      DEBUG=False NOPLOTS=False SAVEALL=True N_JOBS=-1 \
          N=1000  BAYES=True    T=$T         K=$K \
          python3 main.py configuration.py \
      && cp logs/main_py3_log.txt \
              logs/main_py3_log__N1000_BAYES_T{T}_K{K}.txt \
  done; done
    \end{minted}
    \caption{Bash code to run the large experiments presented in Sections~\ref{sec:3:reviewSPAlgorithms} and \ref{sub:3:additionalExperiments}.}
    % \captionof{listing}{Small snippet of Bash code to run an experiment \label{lst:3:BashCodeToLaunchLargeExperiments}.}
    \label{lst:3:BashCodeToLaunchLargeExperiments}
\end{listing}
